Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-12 doc/reviews/ResponseToReviewer1.tex

  \item We have added the following sentence to the start of Section 3
    \begin{quotation}
      All derivatives are computed with spectrally-accurate Fourier
      differentiation.
    \end{quotation}
\end{itemize}

\noindent
\comment{Line 256: you set the strength of the repulsive force $M = 4k_B
T$. In your simulations there is no thermal fluctuations, so why using
$k_B T$ as a reference energy if it is no there in the simulations?
There should be another energy scale that you could use to calibrate
$M$, right?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Related question: how much does the interparticle distance
depend on on the strength and range of this artificial repulsive
potential? What is the impact on the vesicle shape and effective
properties?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Figure 3a,b,d: what does the term in parenthesis ``(1)" means
on the label of the ordinate axis?}
\begin{itemize}
  \item The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
\end{itemize}

\noindent
\comment{Line 302: the authors mention that tank-threading can only be
observed for shear rate as high as $10^{6}\text{s}^{-1}$. Can such a
high value be generated in experiments?}
\begin{itemize}
  \item A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
Since the size of the JP vesicle in this work is much smaller than experimental use vesicles, 
a very high shear rate of the flow is needed to acquire the tank-treading motion.
\end{itemize}

@@

\noindent
\comment{Eq.~4.4, typo: $v$ should be $u$.}
\begin{itemize}
  \item This typo is fixed.
\end{itemize}

\noindent
\comment{Figure 6: the yellow particle is not visible when printing in
black and white.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 388, typo: ``has" should be ``have".}
\begin{itemize}
  \item This typo is corrected.
\end{itemize}

\noindent
\comment{Figure 7a is never referred to and its content is never
discussed in the text.}
\begin{itemize}
  \item Thank you for noticing this missing connection. We added a description connected to Figure 7a.
\end{itemize}

\noindent
\comment{Line 393: The reference to panel ``Figure 7c" seems to be a
typo. Same for ``Figures 7c and 7d" on line 394, I think it should be
``Figures 7b and 7c".}
\begin{itemize}
  \item This typo is corrected.
\end{itemize}

\noindent
\comment{Side question: Is it possible to change the vesicle stretching
modulus and hydraulic permeability independently or are these two
properties linked to each other and how?}
\begin{itemize}
  \item We added a parametric study in new Table 2 and the trend provides an idea about 
how to change vesicle stretching modulus and hydraulic permeability by adjusting the length related parameters or force related parameters. We think that it is possible to have better understanding about the link between all parameters and these physical quantities after more 
convergence study.
\end{itemize}

### 2022-02-12 doc/reviews/ResponseToReviewer2.tex

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
The authors are introducing a novel numerical approach to study vesicles
under flow conditions in two dimensions. The vesicle is modelled as a
collection of amphiphilic Janus particles (JP) interacting with each
other through a hydrophobic attraction potential (HAP) and a short-range
repulsion force to avoid the overlap between particles. Both the
mobility of the particles and the HAP are recast in the form of an
integral equation of the second kind and solved numerically. The authors
presented some results on the deformation and dynamic of a single
vesicle and a pair of vesicles in different type of external flows.
\\ \\
\noindent
The originality of this work stems from coupling the HAP and Stokes
equations through a boundary integral formulation which I personally
find quite interesting. However, numerical models for vesicles and other
class of soft particles in 2D and 3D are already well established in the
literature. Disregarding the 2D nature of the model, I am not fully
convinced on how this approach outperforms the existing models either in
computational performance or in new applications. The authors should
make an extra effort to highlight this. Another weakness of this model,
if I understood correctly, is that the area of the vesicle is not
conserved beyond the small deformation limit. To the best of my
knowledge, a 2D vesicle should fulfill both constant area and perimeter
constraints. This means that the range of application of the model is
limited to the small deformation limits when used to mimic vesicles
under flow. Finally, this paper lacks a thorough validation of the
numerical results with the existing data in the literature and/or an
original application/result describing a physical phenomenon not covered
by the previous literature. This work is suitable for publication in
this journal but a major revision is needed. Below additional minor
comments to be addressed.}
\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
our manuscript. The proposed 2D JP vesicle model has a geometrical property 
of constant perimeter with a finite number of particles. Study of the permeability gives a numerical evidence that the constant area constraint of this enclosed bilayer structure does not apply in this 
work. In response, we performed a number of simulations and provided more parametric study in 
terms of small changes in parameters. 
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

### 2022-02-12 doc/reviews/ResponseToReviewer3.tex

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 3}
\comment{\noindent
The manuscript extends the authors’ previous work on modeling
amphiphilic particles in a viscous solvent to modeling amphiphilic Janus
particles suspended in a viscous background flow. The authors adopted
the GMRES iterative method to solve the screened Laplace equation for
hydrophobic attraction. They investigated the inter-monolayer friction
of vesicles formed by amphiphilic Janus particles and corresponding
membrane ruptures in viscous flows, and simulated the spatial migration
dynamics of a vesicle in a parabolic flow and also the hydrodynamics of
two vesicles in shear and extensional flows.
\\ \\
\noindent
This manuscript presents a systematic study of the hydrodynamics of
vesicles formed by amphiphilic Janus particles in viscous flows. It
provides quantitative analysis of the inter-monolayer friction, membrane
permeability and the migration dynamics of soft suspended vesicles. The
topic on hydrodynamics of complex fluids is interesting, and this
research fits the scope of Journal of Fluid Mechanics. Here, I am in a
favor of its publication at some points if the authors can address the
following concerns in the revised manuscript.
}
\begin{itemize}
  \item We would like to thank the referee for the help with the presentation, which
has been modied as follows.
%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

@@

\item Change: We added a short paragraph to describe our methodology to capture the lubrication flow in the space between particles in close vicinity of each other in page, between lines \$\$\$ and \$\$\$.

\end{itemize}

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated. Therefore the $x$-axis of Fig.~6 represents the time horizon in unit of $\mu$s and 
the $y$-axis represents the $y$ position of the centroid of the JP vesicle.
\end{itemize}

### 2022-02-12 doc/main_jfm.tex
RJR new Figure2_part1_Wrapper.pdf; new permeability section

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}

\subsection{Stretching and Permeability}
\label{sec:ves_in_quiescent}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} In JP vesicles, tension and pressure relax as
  fluid is expelled through the particle interstices. In panel (a), the
  thin curve plots the mean of the norm of the particle translational
  velocities. The thick curve plots the mean of the absolute value of
  the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
  a spatially constant internal pressure 0.05~pN nm$^{-2}$ (red color,
  panel (b)). In panel (c), pressure has dissipated and the vesicle has
  moved from its initial configuration (gray circles), to the
  equilibrium configuration (black circles). The data in panels (d) and
  (e) support the linear relationship expressed by
  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. Circles are for a
  vesicle with 17 nm initial radius; square are for a 34 nm initial
  radius. Asterisks are for a 18 nm initial radius but with smaller,
  1.25 nm diameter particles. In panel (f), the theoretical time course
  \eqref{eq:perm_solution} overlaps the data using constants $K_A$ and
  $P$ derived from panels (d) and (e). }
\end{figure}
Finally, we show that the JP vesicle behaves as a permeable membrane and the inextensibility comes
about due to a large stretching modulus.
%an extensible, permeable membrane. 
Figures~\ref{figure2}b shows an initial, non-equilibrium JP
vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
spatially constant, positive internal pressure (0.05~pN nm$^{-2}$) and the white
shows a spatially constant zero, external pressure. There is some fluid flow and
the pressure vanishes as the configuration tends toward the equilibrium
state (Figures~\ref{figure2}c).

What could be the source of this drop in pressure? In membrane
continuum  mechanics, small changes in surface area give rise to a membrane tension
$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
and $A_0$ is the reference surface area. The area modulus $K_A$ of
bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}). In the
two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. Moreover, stretched, circular vesicles \ReviewerOne{have}
a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R^{-1}$ is the total curvature of the circular
cylinder.

Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
between the particle centre and the far-field (see
Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
the vesicle radius, and the horizontal axis is the relative stretch.
The circles are data for a vesicle with radius 17 nm. The linear fit
(solid lines) shows that $R\Delta P$ is proportional to the relative
stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
radius 34 nm, and the data overlap supports that the proportionality
constant $K_A$ is a stretching modulus that is independent of vesicle
size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
agreement with the experimentally obtained area moduli of lipid bilayer. 
%
The reason the tank-treading vesicle appears inextensible ($L$ is more or less constant in Figure~\ref{figure4}c) is because the modulus $K_A$ is large.
%
To evaluate how changes to particle size lead to different
physical properties, the asterisk symbols are for an 18 nm radius
vesicle consisting of particles with diameter 1.25 nm, instead of the
usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
102$~pN~nm$^{-1}$.

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer, and in membrane mechanics aqueous flux is quantified by the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}). Figure~\ref{figure2}e shows that the data for
$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by
\eqref{eq:perm}. The slopes of the linear fits give the hydraulic
permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$
nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
respectively. Like the area modulus, the data give a permeability 
that is independent of vesicle size.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
  interact by orbiting about the origin. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. The fluid velocity streamlines appear in
  grey.  The dimensionless shear rate is $\chi=0.005$.}
\end{figure}

The hydraulic permeability we calculate, however, is not in agreement
with experimentally derived values and is larger by a few orders of
magnitude. We suspect this discrepancy is due to inter-particle distance
of the JP being large compared to the inter-lipid spacing in real
bilayers. To test this, we calculate the permeability for the particles
with diameter 1.25 nm. Due to their smaller size but fixed repulsion
strength, these particles have a larger inter-particle spacing resulting
in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
(Figure~\ref{figure2}e, asterisk symbols).

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data (Figure~\ref{figure2}f).

% table 2

\begin{table}
\caption{Stretching Moduli and Permeabilities}
\centering
\begin{tabular}{ c c c c c c c }
 radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
\hline      \hline 
 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
%
 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
%
 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
%
 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
%
 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
\end{tabular} 
\label{table2}
\end{table}
%

\ReviewerOne{Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases. The default setup is shown in the first row. The next two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$. One can observe that the constant $K_A$ increases 
and $P$ decreases as size of particles decreases. 
The last two rows demonstrate the results when the force related parameters $\gamma$ and $M$ are adjusted by 5$\%$ and 10$\%$. The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases. As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP. However, the detailed correlation between all model parameters will be explored as 
a direction of future work.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Two Vesicles in a Linear Flow}

\begin{figure}
  \centering
\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
%\includegraphics[height=2in]{N116_shear_0.pdf}
%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
%\includegraphics[height=2in]{N116_shear_5000.pdf}
%\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} 
  The figure is for the same simulation as in Figure~\ref{figure9}, 
  but also plots the fluid pressure $p$. The color bar is identical for all panels. 
  Internal pressure is initially zero, but then grows as the vesicles come close to contact  (panel (c)).
  The insets are generated from simulations of a continuum model of the vesicles (\cite{qua-vee-you2019}). 
  The streamlines of the two models are in agreement.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Stretching and Permeability}
\label{sec:ves_in_quiescent}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_part1_Wrapper.pdf}
\caption{\label{figure2part1} Tension and pressure relax as
  fluid is expelled through the particle interstices. In panel (a), inset, 
  pressure is spatially constant inside the JP vesicle (inset). and 
  Laplace pressure ((a), squares) and excess length ((b), squares) dissipate exponentially.  
  The data in panels (b) and (c) show a linear relationship expressed by
  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. }
\end{figure}

In this section, we consider a circular JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
We show that the JP particle bilayer behaves as an inextensible, permeable membrane with
the inextensibility coming from a large stretching modulus.

In membrane continuum  mechanics, changes in membrane surface area $A$ give rise to a tension
$\tilde \sigma = K_A(A/A_0 - 1)$ where $A_0$ is the reference surface area \cite{NaTr00}. 
For a two-dimensional membrane, the tension is 
\begin{align}
\label{eq:stretch}
\tilde \sigma = K_A\left(L/L_0 - 1 \right),
\end{align}
where $L$ and $L_0$ are arc length and resting length,
respectively. 
Membrane tension gives rise to 
a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \tilde \sigma/R,
\end{align}
where $\Delta p$ is the jump in far-field pressure to internal pressure and
$R = L/2\pi$.
In order to relieve Laplace pressure, 
water flows across the membrane. The rate of efflux is governed by  
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = - P\Delta p,
\end{align}
where $P = k/(\mu \Delta x)$ is a constant, $k$ is hydraulic permeability, 
$\mu$ is the solvent viscosity, and $\Delta x$ is the 
membrane thickness, about 5 nm
(\cite{chabanon2017, qua-gan-you2021}).

Our  simulation setup consists of an initial, non-equilibrium JP
obtained by dilating the equilibrium shape outward (Figures~\ref{figure2part1}a).
At $t = 0$, pressure \eqref{eq:stokes} is spatially constant  inside and outside the vesicle 
(Figures~\ref{figure2part1}a, inset)
and Laplace pressure decreases to zero exponentially 
(Figures~\ref{figure2part1}a,  squares).  
At the same time, arc length decreases from its initial value $L(0)$ to its resting length $L_0$
(Figures~\ref{figure2part1}b).

To evaluate whether JP vesicles possess a stretching modulus,
Figure~\ref{figure2part1}c plots $R \Delta p$ against the excess length $L/L_0 - 1$.  The squares
are for the baseline simulation with vesicle diameter about 34 nm.  The diamonds 
are for a vesicle with twice the diameter.  The linear relationships 
are independent of vesicle size and give an area modulus $K_A = 170 \pm 9$ pN nm$^{-1}$.
 This relatively large stretching modulus is the reason why the JP vesicle conserves length in the 
shear-flow simulations (Figure \ref{figure2part1}c).
The value also reasonably agrees with stretching moduli for 
lipid bilayers, around $240$ pN nm$^{-1}$ \cite{NaTr00}.

 In the initial, dilated vesicle,
contractile motion is limited by the incompressibility of the 
fluid bound by the vesicle.  
Hence, the Laplace pressure 
comes from an excess in inter-particle separation.  The vesicle-bound water,
however, can escape through the gaps between the particles and this
is how the JP vesicle relieves Laplace pressure over time (Figure \ref{figure2part1}a).

To evaluate the rate of water outflow, 
Figure~\ref{figure2part1}d plots the the simulation values for $dA/dt$.  
These values are proportional to $L\Delta p$ and like for the stretching modulus, 
the proportionality constants are 
independent of vesicle size.
The  linear fits give a hydraulic permeability $P = 0.0290 \pm 0.007$ nm$^3$ ns$^{-1}$ pN$^{-1}$.
We can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm} to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
Using the fitted values for $P$ and $K_A$, the theoretical time course for 
\eqref{eq:perm_solution} (Figure~\ref{figure2part1}b, solid curve) is in good
agreement with the JP data (Figure~\ref{figure2part1}b, squares).

Our value for permeability disagrees 
with permeabilities for lipid bilayers by a few orders of magnitude  (\cite{chabanon2017, qua-gan-you2021}).
Potential reasons for this include the following. 
Our two-dimensional simulations correspond to water flowing past a collection
of parallel cylinders, which has a larger permeability than for a collection
of spheres of comparable radius.   
Second, permeability vanishes with inter-particle separation.  
However, in our simulations, inter-particle separation is intentionally made comparable to 
particle radius to avoid aggresive mesh refinement.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
\caption{\label{figure2}  
The ratios of the abscissa and ordinates from Figure \ref{figure2part1}c, d are well-fit by constant functions (baseline, dots).
The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
The x's and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
The variable $x$ is used to denote the horizontal axis coordinate. 
}
\end{figure}

\begin{table}
\caption{Stretching Moduli and Permeabilities}
\centering
\begin{tabular}{ c c c |c c| c |c }
 radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
\hline      \hline 
 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
%
 \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
%
 \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
%
 \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
%
 \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
\end{tabular} 
\label{table2}
\end{table}
%

We performed a parametric study of the dependence of $K_A$ and $P$
on model parameters taking into account   
(i) changes in interfacial strength and (ii) changes in size.
Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
 The baseline setup is shown in the first row.
The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by $c$, 
we can related the scaled energy to that of the baseline case by 
\[E_c(x) = c(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
quantity varies proportionally with $c$.

One can observe that $K_A$ increases and $P$ decreases as the length scale decreases. 
The decrease in  $P$ is expected because 
the size of the gap between adjacent JP particles is directly proportional to length scale.
To give a more detailed account, pressure $p$ and water flux across the membrane $q$ scale as 
$p_{\lambda}(\mathbf{x}) = \lambda^{-1} p(\mathbf{x}/\lambda)$ and 
$q_{\lambda}(\mathbf{x}) = q(\mathbf{x}/\lambda)$ 
when $l_0$ is scaled by $\lambda$. As a result, the scaled permeability constant satisfies 
\[
P_{\lambda} = q_{\lambda}/\Delta p_{\lambda} = q/(\lambda^{-1} \Delta p) = \lambda P.
\]
For the stretching modulus, the total energy transforms as 
\[E_{\lambda}(x) = \lambda G(x/\lambda) + H(x/\lambda ).\]
The factor $\lambda$ comes from the change of 
variables formula for the integral in \eqref{eq:baseline_energy}.
The stretching modulus increases because $\frac{d^2E_{\lambda}}{dx^2}$ increases with decreases in $\lambda.$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
  interact by orbiting about the origin. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. The fluid velocity streamlines appear in
  grey.  The dimensionless shear rate is $\chi=0.005$.}
\end{figure}
\subsection{Two Vesicles in a Linear Flow}
\begin{figure}
  \centering
\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
%\includegraphics[height=2in]{N116_shear_0.pdf}
%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
%\includegraphics[height=2in]{N116_shear_5000.pdf}
%\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} 
  The figure is for the same simulation as in Figure~\ref{figure9}, 
  but also plots the fluid pressure $p$. The color bar is identical for all panels. 
  Internal pressure is initially zero, but then grows as the vesicles come close to contact  (panel (c)).
  The insets are generated from simulations of a continuum model of the vesicles (\cite{qua-vee-you2019}). 
  The streamlines of the two models are in agreement.}
\end{figure}
